Verifying Spatial Properties of Array Computations

### 2017-04-17 oopsla17/algorithms.tex
Fix the subset rel of Region and use macro for region

In the model, we can regard both array indices and specifications as groups of
points in $N$-dimensional space. Notion of consistency is then intuitively
whether these two (potentially infinite) sets of points in space match or not.
This leads to a simple set based consistency function defined as
%
\begin{align*}
  \mathit{consistent} & :
    \mathsf{Mult}(\mathcal{P}(\mathcal{P}(\bz{})^N)) \times
    \mathsf{Mult}(\mathsf{Approx}(\region{N})) \to \mathbb{B} & \\
%
  \mathit{consistent}(\mathit{ix}, \mathit{model}) & = \begin{cases}
    \mathsf{false} & \mathit{model} = \mathsf{once}(x) \wedge ix = \mathsf{mult}(y) \\
    \mathit{consistent'}(\mathit{peel}(ix), \mathit{peel}(model)) & \textit{otherwise}
  \end{cases} \\
%
  \mathit{consistent'} & :
    \mathcal{P}(\mathcal{P}(\bz{})^N) \times
    \mathsf{Approx}(\region{N}) \to \mathbb{B} & \\
%
  \mathit{consistent'}(\mathit{ix}, \mathit{model}) & = \begin{cases}
    m = \mathit{ix} & \mathit{model} = \mathsf{exact}(m) \\
    m \supseteq \mathit{ix} & \mathit{model} = \mathsf{upper}(m) \\
    m \subseteq \mathit{ix} & \mathit{model} = \mathsf{lower}(m)
  \end{cases}
\end{align*}
%
The first function, $\mathit{consistent}$, checks whether the linearity of the
specification matches that of the indices, \ie{} if the specification allows
indices to be repeated or not.Then it delegates to $\mathit{consistent'}$
function which checks if the points observed in the array expression matches
the space defined by the specification. Lower bounds, marked by \texttt{atLeast}
modifier, require the space defined by the specification to remain inside the
set of indices, while an upper bound, market by \texttt{atMost} modifier,
requires the opposite: enclosure. In the absence of such modifiers, we expect
the space defined by observed indices correspond exactly those defined by the
region in the specification, hence requiring set equality.

@@

\subsubsection{Covering}
A covering of (possibly overlapping) the subscript space
is calculated as a value of $Region_N$. This is computed iteratively
by the following steps until a fixed-point is reached:

@@

For our example:
%
\begin{align*}
\textsf{coalesce}(\mathcal{S}_0) & =
\{[-1,0] \times [0,0],\,[0,0] \times [-1, 0],\,[0,0] \times [0,1],\,[0,1]
  \times [0,0]\} \\
%\textsf{nonOverlap}(\textsf{coalesce}(\mathcal{S}_0)) & =
%                                                        \textsf{coalesce}(\mathcal{S}_0)
%  \\
\textsf{coalesce}^2(\mathcal{S}_0) & =
\{[-1, 1] \times [0, 0],\,[0, 0] \times [-1, 1]\}
\end{align*}
%
The fixed-pointed is reached within two applications of
\textsf{coalesce} for our example.
\dnote{We probably need to say something about classifying index
schemes are \textit{Region$_N$}?}

>>>>

In the model, we can regard both array indices and specifications as groups of
points in $N$-dimensional space. Notion of consistency is then intuitively
whether these two (potentially infinite) sets of points in space match or not.
This leads to a simple set based consistency function defined as
%
\begin{align*}
  \mathit{consistent} & :
    \mathsf{Mult}(\mathcal{P}(\bz{}^N) \times
    \mathsf{Mult}(\mathsf{Approx}(\region{N})) \to \mathbb{B} & \\
%
  \mathit{consistent}(\mathit{ix}, \mathit{model}) & = \begin{cases}
    \mathsf{false} & \mathit{model} = \mathsf{once}(x) \wedge ix = \mathsf{mult}(y) \\
    \mathit{consistent'}(\mathit{peel}(ix), \mathit{peel}(model)) & \textit{otherwise}
  \end{cases} \\
%
  \textit{consistent'} & :
    \mathcal{P}(\bz{}^N) \times
    \mathsf{Approx}(\region{N}) \to \mathbb{B} & \\
%
  \textit{consistent'}(\mathit{ix}, \mathit{model}) & = \begin{cases}
    m = \mathit{ix} & \mathit{model} = \mathsf{exact}(m) \\
    m \supseteq \mathit{ix} & \mathit{model} = \mathsf{upper}(m) \\
    m \subseteq \mathit{ix} & \mathit{model} = \mathsf{lower}(m)
  \end{cases}
\end{align*}
%
The first function, $\mathit{consistent}$, checks whether the linearity of the
specification matches that of the indices, \ie{} if the specification allows
indices to be repeated or not.Then it delegates to $\mathit{consistent'}$
function which checks if the points observed in the array expression matches
the space defined by the specification. Lower bounds, marked by \texttt{atLeast}
modifier, require the space defined by the specification to remain inside the
set of indices, while an upper bound, market by \texttt{atMost} modifier,
requires the opposite: enclosure. In the absence of such modifiers, we expect
the space defined by observed indices correspond exactly those defined by the
region in the specification, hence requiring set equality.

@@

\subsubsection{Covering}
A covering of (possibly overlapping) the subscript space
is calculated as a value of \region{N}. This is computed iteratively
by the following steps until a fixed-point is reached:

@@

For our example:
%
\begin{align*}
\textsf{coalesce}(\mathcal{S}_0) & =
\{[-1,0] \times [0,0],\,[0,0] \times [-1, 0],\,[0,0] \times [0,1],\,[0,1]
  \times [0,0]\} \\
%\textsf{nonOverlap}(\textsf{coalesce}(\mathcal{S}_0)) & =
%                                                        \textsf{coalesce}(\mathcal{S}_0)
%  \\
\textsf{coalesce}^2(\mathcal{S}_0) & =
\{[-1, 1] \times [0, 0],\,[0, 0] \times [-1, 1]\}
\end{align*}
%
The fixed-pointed is reached within two applications of
\textsf{coalesce} for our example.
\dnote{We probably need to say something about classifying index
schemes are \region{N}?}
